---
title: "Lab 00 - Hello IDS!"
author: "David Mullender"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Peter Rabbit", "David", "member 2", 
           "member 3", "member 4"),
  github_username = c("mcgregors-garden", "davidmullender", "username 2", 
                      "username 3", "username 4"), 
  colour = c("powderblue", "green4", "colour 3", 
             "colour 3", "colour 4"),
  hobby = c("Hopping", "hobby 1", "hobby 1", 
            "hobby 1", "hobby 4"),
  favourite_number = c(2, 7, NA, NA, NA)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


Each team members favourite number, with their bar colour representing their favourite colour

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "GitHub username", 
          y = "Favourite number",
          title = "Team Data")
```


### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

It would not be a good way of conveying information, as there would be a wide variety of different hobbies, so there would be a large number of bars on the graph, with most of the values just being 1.
